In this assignment, we gathered and prepared the necessary data for analyzing the Healthcare sector within the Euro Stoxx 600
index. 
The data includes total return indices for individual stocks, risk-free interest rates, and the market index for the
healthcare sector.

\section{Data Collection}
\begin{itemize}
    \item \textbf{Total Return Indices:} We obtained the total return indices for ten companies within the Healthcare sector.
    These companies were selected based on the availability of complete data from 2000 to 2024.
    \item \textbf{Market Index:} The Euro Stoxx 600 Health Care index was used as a benchmark for the overall market performance
    within the sector.
    \item \textbf{Risk-Free Rates:} Monthly risk-free interest rates were derived from annualized Federal Reserve data to
    compute excess returns.
\end{itemize}

\section{Data Preparation}

\begin{itemize}
    \item \textbf{Return Calculation:} Monthly returns were calculated using logarithmic differences in prices. This method 
    ensures that the data is approximately normally distributed and facilitates economic interpretation.
    \item \textbf{Excess Returns:} Stock and market returns were adjusted by subtracting the risk-free rate, consistent with the 
    CAPM framework.
    \item \textbf{Data Quality Checks:} The datasets were thoroughly examined for missing or duplicate values to ensure the 
    robustness of subsequent analyses.

\end{itemize}

\section{Preliminary Visualization}
Scatter plots were created to examine the relationship between stock excess returns and market excess returns. 
These plots showed a clear linear relationship for most equities, supporting the applicability of the CAPM. 
However, some observations indicated potential outliers, which will be analyzed further in later steps.